\documentclass[12pt,oneside]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}

\begin{document}

\begin{flushleft}

MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims \\
\today

\vspace{0.3in}

Austin Knudsen \\
Attorney General \\
State of Montana \\
Department of Justice \\
215 North Sanders Street \\
Helena, MT 59601

\vspace{0.3in}

\textbf{RE: Comprehensive State Criminal Prosecution Referral} \\
\textbf{Danielle Chard, E'Lise Chard, YWCA Missoula Officials, MPD Officers} \\
\textbf{Perjury, Criminal Defamation, Conspiracy, Institutional Corruption} \\
\textbf{Pattern Affecting Multiple Victims (2015--2025)}

\vspace{0.3in}

Dear Attorney General Knudsen:

\vspace{0.2in}

MISJustice Alliance respectfully submits this comprehensive criminal prosecution referral documenting systematic violations of Montana criminal law by individual perpetrators (Danielle Christine Chard, E'Lise Marie Chard) and institutional actors (YWCA Missoula officials, Missoula Police Department officers). While the majority of evidence focuses on crimes against Elvis Ryland Nuno, the submitted documentation establishes \textbf{beyond reasonable doubt} a pattern of endemic corruption affecting numerous Montana residents and warranting expanded criminal investigation.

\section*{INDIVIDUAL PERPETRATORS}

\subsection*{Danielle Christine Chard (DOB: 09/23/1983)}

\textbf{Criminal Defamation (MCA 45-8-212/213):}

\begin{itemize}
\item False statements to law enforcement across multiple jurisdictions.
\item Malicious intent to damage reputation and standing.
\item Knowledge of falsity demonstrated through contradictory statements.
\item Pattern spanning 2015--2025.
\end{itemize}

\textbf{Perjury (MCA 45-7-202):}

\begin{itemize}
\item False sworn statements in court proceedings.
\item Contradicted by documentary evidence and witness testimony.
\item Material to legal proceedings.
\end{itemize}

\textbf{Criminal Conspiracy (MCA 45-4-102):}

\begin{itemize}
\item Coordination with sister E'Lise Chard.
\item Agreement to commit criminal defamation and false reporting.
\item Overt acts in furtherance of conspiracy.
\end{itemize}

\subsection*{E'Lise Marie Chard (DOB: 09/23/1983)}

\textbf{Perjury and False Swearing (MCA 45-7-202):}

\begin{itemize}
\item False statements to law enforcement.
\item Fabricated ``stalking'' allegations.
\item Contradicted by electronic evidence and timestamps.
\end{itemize}

\textbf{Criminal Defamation (MCA 45-8-212/213):}

\begin{itemize}
\item False public statements damaging reputation.
\item Coordination with YWCA position to amplify false claims.
\item Malicious intent demonstrated through retaliatory pattern.
\end{itemize}

\textbf{Intimidation (MCA 45-5-203):}

\begin{itemize}
\item Retaliation following formal YWCA complaint.
\item Coordination with law enforcement to threaten and coerce.
\item First Amendment violations through institutional power abuse.
\end{itemize}

\section*{INSTITUTIONAL ACTORS}

\subsection*{YWCA Missoula Officials}

The enclosed \textbf{YWCA Institutional Corruption Supplemental} documents criminal conduct \textbf{independent of the Nuno case}:

\begin{itemize}
\item \textbf{Fraud:} Misrepresentation to federal grant agencies (\$500,000+ documented).
\item \textbf{Breach of Fiduciary Duty:} Board governance violations (Detective Brueckner conflict).
\item \textbf{Obstruction of Justice:} Suppression of complaints and retaliation against complainants.
\item \textbf{Criminal Defamation:} False court filings (Arthur Brown case---separating father from children).
\end{itemize}

\subsection*{Missoula Police Department}

\textbf{Detective Connie Brueckner:}

\begin{itemize}
\item Undisclosed conflict of interest (YWCA Board + lead investigator).
\item Fourth Amendment violations (warrantless searches).
\item False imprisonment and abuse of authority.
\item Obstruction of justice (Brady violations).
\end{itemize}

\textbf{Officer Ethan Smith:}

\begin{itemize}
\item Harassment of Nuno family members.
\item Abuse of police powers for personal benefit.
\item Removed for ``obvious impropriety'' but no criminal prosecution.
\end{itemize}

\section*{PATTERN BEYOND NUNO CASE}

Evidence establishes systematic institutional corruption affecting multiple victims:

\textbf{Multiple Victim Accounts (YWCA):}

\begin{itemize}
\item Arthur Brown: Fraudulent court filings interfering with parental rights.
\item Anonymous clients: HIPAA violations, ADA discrimination, service discrimination.
\item Employees: Pattern of exploitation, unsafe conditions, organizational dysfunction.
\end{itemize}

\textbf{Federal Context:}

\begin{itemize}
\item 2012--2016 DOJ investigation (Missoula ``rape capital'').
\item 2023 LifeGuard Group strip search allegations (no prosecution despite DOJ agent concerns).
\item Systematic failure of local oversight mechanisms.
\end{itemize}

\section*{REQUESTED STATE ACTIONS}

\begin{enumerate}
\item \textbf{Criminal Prosecution:} Danielle Chard and E'Lise Chard for perjury, criminal defamation, conspiracy, intimidation, and related offenses.
\item \textbf{Institutional Investigation:} YWCA Missoula for fraud, breach of fiduciary duty, obstruction.
\item \textbf{Law Enforcement Investigation:} Detective Brueckner and Officer Smith for civil rights violations and abuse of authority.
\item \textbf{Grand Jury:} Impaneling for institutional corruption investigation.
\item \textbf{Professional Sanctions:} Coordination with licensing boards (law enforcement, social work).
\item \textbf{Nonprofit Oversight:} Coordination with Montana Secretary of State and relevant regulators for governance violations.
\end{enumerate}

\section*{SUBMISSION CONTENTS (11 Documents)}

\begin{enumerate}
\item Case Summary.
\item FBI Seattle Civil Rights Cover Letter (federal RICO and civil rights coordination).
\item FBI Montana Field Office Civil Rights Cover Letter (Montana-focused).
\item This Montana Attorney General Cover Letter.
\item Washington Attorney General Cover Letter.
\item U.S. Attorney, District of Montana Cover Letter.
\item U.S. Attorney, Western District of Washington Cover Letter.
\item DOJ Public Integrity Section Cover Letter.
\item Danielle Chard Criminal Report.
\item E'Lise Chard Criminal Report.
\item YWCA Institutional Corruption Supplemental, Elvis Nuno Sworn Declaration, and comprehensive evidentiary documentation.
\end{enumerate}

\section*{COORDINATION}

This submission is being made concurrently to:

\begin{itemize}
\item FBI Seattle Field Office Civil Rights squad.
\item U.S. Attorney, District of Montana.
\item U.S. Attorney, Western District of Washington.
\item Washington State Attorney General (Civil Rights Division).
\item DOJ Criminal Division, Public Integrity Section.
\end{itemize}

Federal and state prosecutions can proceed simultaneously with appropriate coordination.

\section*{URGENCY}

\begin{itemize}
\item Statute of limitations concerns for some violations.
\item Ongoing criminal activity affecting vulnerable populations.
\item Evidence preservation needs.
\item Public safety threats from institutional dysfunction.
\item Victims facing continued retaliation.
\end{itemize}

We respectfully request an initial response via digital communication outlining appropriate next steps, sent to \texttt{advocacy@misjusticealliance.org}, so that prosecution strategy and coordination with federal investigators can proceed while protecting the anonymity and safety of MISJustice Alliance members and reporting victims; this packet reflects thousands of hours of collaborative work, extensive deep records research, and interviews with multiple victims, and the evidence is comprehensive and ready for immediate grand jury presentation.

\vspace{0.3in}

\noindent
Respectfully submitted,

\vspace{0.3in}

\noindent
MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims

\vspace{0.2in}

\noindent
Contact: [\textit{Contact information will be provided only through MISJustice Alliance after the receiving office confirms a concrete plan to prevent any retaliation or adverse action against reporting victims and witnesses.}]

\end{flushleft}

\end{document}
