\documentclass[12pt,oneside]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}

\begin{document}

\begin{flushleft}

MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims \\
\today

\vspace{0.3in}

Bob Ferguson \\
Attorney General \\
State of Washington \\
Office of the Attorney General \\
1125 Washington Street SE \\
Olympia, WA 98504

\vspace{0.3in}

\textbf{RE: Interstate Criminal Coordination Investigation Referral} \\
\textbf{Prosecutorial Misconduct, Evidence Alteration, Interstate Conspiracy} \\
\textbf{King County Prosecutors, Seattle/Edmonds Police, Montana Coordination} \\
\textbf{OPA Case 2016OPA-1167 Evidence Falsification}

\vspace{0.3in}

Dear Attorney General Ferguson:

\vspace{0.2in}

MISJustice Alliance respectfully submits this comprehensive investigation referral documenting interstate criminal coordination between Washington State and Montana law enforcement agencies, prosecutorial misconduct, and systematic civil rights violations affecting Elvis Ryland Nuno and potentially other victims. This submission requests state investigation of Washington-based actors and coordination with federal and Montana authorities investigating broader institutional corruption.

\section*{WASHINGTON STATE CRIMINAL CONDUCT}

\subsection*{Danielle Christine Chard (Seattle/Edmonds Resident)}

\textbf{Washington Criminal Violations:}

\begin{itemize}
\item \textbf{Perjury (RCW 9A.72.020):} False sworn statements in court proceedings.
\item \textbf{Making False Statement (RCW 9A.76.175):} False reports to law enforcement.
\item \textbf{Witness Tampering (RCW 9A.72.085):} Coordination to manufacture false testimony.
\item \textbf{Interstate Conspiracy:} Coordination with Montana actors for false prosecution.
\end{itemize}

\subsection*{Prosecutorial Misconduct}

\textbf{King County Prosecutors:}

\begin{itemize}
\item Charges filed without probable cause.
\item Excessive bail demands (\$50,000--\$100,000 for misdemeanors).
\item Suppression of exculpatory evidence.
\item Coordination with Montana prosecutors despite lack of legitimate basis.
\item Malicious prosecution pattern (2015--2020).
\end{itemize}

\subsection*{OPA Case 2016OPA-1167: Evidence Alteration}

Critical misconduct documented:

\begin{itemize}
\item Seattle Office of Professional Accountability received complaint of police report falsification.
\item OPA investigation found ``inconsistencies'' in police reports.
\item Case closure letter acknowledged report alterations but declined prosecution.
\item Pattern of accountability failures enabling continued misconduct.
\end{itemize}

\section*{INTERSTATE COORDINATION PATTERN}

Evidence establishes coordinated criminal activity across state lines:

\begin{itemize}
\item Washington charges filed based on Montana false reports.
\item Montana charges filed based on Washington false reports.
\item Prosecutors coordinating despite lack of legitimate nexus.
\item Information sharing violating privacy protections.
\item Systematic harassment across jurisdictional boundaries.
\end{itemize}

\section*{BROADER INSTITUTIONAL CORRUPTION}

While the Nuno case provides detailed Washington evidence, the comprehensive submission establishes a pattern extending to Montana institutional actors:

\textbf{YWCA Missoula Institutional Corruption Supplemental (Document \#11):}

\begin{itemize}
\item Multiple victim accounts independent of the Nuno case.
\item Federal grant fraud (\$500,000+ documented).
\item HIPAA violations endangering domestic violence survivors.
\item Detective Connie Brueckner conflict (YWCA Board + lead investigator).
\item Pattern spanning 2012--2025.
\end{itemize}

\textbf{Implications for Washington:}

\begin{itemize}
\item Interstate coordination with corrupt institutional actors.
\item Washington prosecutors relying on false information from Montana.
\item Potential pattern affecting other interstate cases.
\item Systematic failure of oversight mechanisms.
\end{itemize}

\section*{REQUESTED ACTIONS}

\begin{enumerate}
\item \textbf{Criminal Investigation:} Danielle Chard for perjury, false statements, witness tampering, and related offenses under Washington law.
\item \textbf{Prosecutorial Review:} Investigation of King County prosecutorial misconduct, excessive bail, and malicious prosecution.
\item \textbf{OPA Investigation Review:} Review of 2016OPA-1167 closure decision and accountability failures.
\item \textbf{Interstate Coordination Analysis:} Examination of improper information sharing with Montana agencies.
\item \textbf{Civil Rights Division Review:} Systematic constitutional violations involving Washington actors.
\item \textbf{Professional Discipline:} Coordination with the Washington State Bar and other licensing authorities regarding prosecutor misconduct.
\end{enumerate}

\section*{FEDERAL COORDINATION}

This submission is concurrent with:

\begin{itemize}
\item FBI Seattle Field Office Civil Rights squad (federal RICO and civil rights investigation).
\item U.S. Attorney, Western District of Washington (federal jurisdiction for Washington-based crimes).
\item U.S. Attorney, District of Montana (interstate coordination).
\item Montana Attorney General (state prosecution in Montana).
\item DOJ Criminal Division, Public Integrity Section (public corruption and prosecutorial misconduct).
\end{itemize}

Washington Attorney General coordination with federal authorities is essential for comprehensive accountability.

\section*{SUBMISSION CONTENTS (11 Documents)}

\begin{enumerate}
\item Executive Summary / Case Summary.
\item FBI Seattle Field Office Civil Rights Cover Letter (Washington-focused).
\item FBI Montana Field Office Civil Rights Cover Letter (Montana-focused).
\item Montana Attorney General Cover Letter.
\item This Washington Attorney General Cover Letter.
\item U.S. Attorney, District of Montana Cover Letter.
\item U.S. Attorney, Western District of Washington Cover Letter.
\item DOJ Public Integrity Section Cover Letter.
\item Danielle Chard Criminal Report.
\item E'Lise Chard Criminal Report.
\item YWCA Institutional Corruption Supplemental, Elvis Nuno Sworn Declaration, and comprehensive evidentiary documentation.
\end{enumerate}

\section*{VICTIM IMPACT}

Elvis Nuno (Washington resident):

\begin{itemize}
\item 11+ years of systematic harassment across WA and MT.
\item False prosecutions in Seattle, Edmonds, and King County.
\item Career destruction in the telecommunications field.
\item Approximately \$2.1 million in lost income.
\item Forced relocation fleeing interstate persecution.
\item Severe psychological trauma and emotional distress.
\item \$6.4--8.4 million in time-barred civil rights claims due to prior attorney malpractice.
\end{itemize}

\section*{URGENCY}

\begin{itemize}
\item Statute of limitations concerns.
\item Ongoing interstate coordination potentially affecting other victims.
\item Evidence preservation needs.
\item Federal investigation coordination requirements.
\item Victim safety concerns from continued retaliation threats.
\end{itemize}

We respectfully request an initial response via digital communication outlining appropriate next steps, sent to \texttt{advocacy@misjusticealliance.org}, so that investigation scope, federal coordination, and Washington State’s role in achieving comprehensive accountability for interstate criminal conspiracy can be determined while protecting the anonymity and safety of MISJustice Alliance members and reporting victims; this packet reflects thousands of hours of collaborative work, extensive deep records research, and interviews with multiple victims, and the evidence is comprehensive and ready for immediate grand jury presentation.

\vspace{0.3in}

\noindent
Respectfully submitted,

\vspace{0.3in}

\noindent
MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims

\vspace{0.2in}

\noindent
Contact: [\textit{Contact information will be provided only through MISJustice Alliance after the receiving office confirms a concrete plan to prevent any retaliation or adverse action against reporting victims and witnesses.}]

\end{flushleft}

\end{document}
