\documentclass[12pt,oneside]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}

\begin{document}

\begin{flushleft}

MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims \\
\today

\vspace{0.3in}

Jesse Laslovich \\
United States Attorney \\
District of Montana \\
Federal Building \\
2601 2nd Avenue North, Suite 3200 \\
Billings, MT 59101

\vspace{0.3in}

\textbf{RE: Federal RICO and Civil Rights Prosecution Authorization Request} \\
\textbf{18 U.S.C. § 1962: Pattern of Racketeering Activity} \\
\textbf{YWCA Missoula Criminal Enterprise, Interstate Conspiracy} \\
\textbf{Grand Jury Impaneling Request}

\vspace{0.3in}

Dear U.S. Attorney Laslovich:

\vspace{0.2in}

MISJustice Alliance respectfully requests federal RICO and civil rights prosecution authorization for a documented criminal enterprise involving YWCA Missoula, Missoula Police Department, associated officials, and interstate co-conspirators. The submitted evidence establishes \textbf{beyond reasonable doubt} a pattern of racketeering activity spanning 2012--2025, affecting multiple victims, and warranting federal grand jury investigation.

\section*{RICO ENTERPRISE ELEMENTS}

\subsection*{Enterprise (18 U.S.C. § 1961(4))}

\textbf{Legal Entity:} YWCA Missoula (Montana nonprofit corporation).

\textbf{Associated Actors:}

\begin{itemize}
\item Missoula Police Department (Detective Connie Brueckner, Officer Ethan Smith, supervisors).
\item Missoula County Prosecutor's Office.
\item King County (WA) Prosecutor's Office.
\item Individual perpetrators (Danielle Chard, E'Lise Chard).
\end{itemize}

\textbf{Continuity:} Ongoing criminal activity (2012--present).

\textbf{Structure:} YWCA Board governance providing organizational framework for coordinated criminal activity.

\subsection*{Pattern of Racketeering Activity (18 U.S.C. § 1961(5))}

\textbf{Predicate Acts (20+ documented):}

\begin{enumerate}
\item \textbf{Mail/Wire Fraud (18 U.S.C. § 1341/1343):}
  \begin{itemize}
  \item Federal grant applications with false representations.
  \item Sponsor reporting misrepresenting services and outcomes.
  \item Interstate wire communications in furtherance of fraud.
  \end{itemize}
\item \textbf{Obstruction of Justice (18 U.S.C. § 1503):}
  \begin{itemize}
  \item Evidence suppression and Brady violations.
  \item Complaint suppression and retaliation.
  \item Cover-up of strip search allegations (LifeGuard Group).
  \end{itemize}
\item \textbf{HIPAA Violations (42 U.S.C. § 1320d-6):}
  \begin{itemize}
  \item Criminal disclosure of protected health information.
  \item Systematic confidentiality breaches.
  \item Pattern affecting multiple clients.
  \end{itemize}
\item \textbf{Witness Tampering (18 U.S.C. § 1512):}
  \begin{itemize}
  \item Intimidation of complainants.
  \item Retaliation against YWCA complaint filers.
  \item Coordination to suppress testimony.
  \end{itemize}
\item \textbf{Interstate Criminal Activity:}
  \begin{itemize}
  \item Coordination between Montana and Washington prosecutors.
  \item Interstate communications in furtherance of false prosecution.
  \item Multi-state conspiracy to deprive civil rights.
  \end{itemize}
\end{enumerate}

\section*{PATTERN BEYOND NUNO CASE}

The \textbf{YWCA Institutional Corruption Supplemental} (Document \#11) establishes RICO predicates \textbf{independent of Elvis Nuno's victimization}:

\subsection*{Multiple Victim Accounts}

\begin{itemize}
\item \textbf{Arthur Brown:} Fraudulent court filings interfering with parental rights.
\item \textbf{Anonymous Client \#1:} HIPAA violations, counseling information leaked to abuser.
\item \textbf{Anonymous Client \#2:} Federal grant fraud, discriminatory services.
\item \textbf{Multiple Employees:} Systematic exploitation, dangerous conditions.
\end{itemize}

\subsection*{Federal Oversight Failures}

\begin{itemize}
\item 2012--2016 DOJ investigation (Missoula ``rape capital'').
\item YWCA designated as reform partner despite governance conflicts.
\item 2023 LifeGuard Group investigation closed without prosecution.
\item Systematic failure of federal grant oversight.
\end{itemize}

\section*{INTERSTATE COMMERCE IMPACT}

\begin{itemize}
\item Federal funding fraud (\$500,000+ documented).
\item Interstate wire communications.
\item Multi-state conspiracy affecting commerce.
\item Deprivation of federally-protected civil rights.
\end{itemize}

\section*{DAMAGES \& FORFEITURE}

\textbf{Total Documented Damages:} \$60+ million.

\begin{itemize}
\item Nuno case: \$6M base × 3 (RICO treble) = \$18M.
\item Institutional victims: \$42.8M+ (conservative estimate).
\end{itemize}

\textbf{Asset Forfeiture (18 U.S.C. § 1963):}

\begin{itemize}
\item YWCA Missoula enterprise proceeds.
\item Federal grant funds obtained through fraud.
\item Property derived from racketeering activity.
\end{itemize}

\section*{REQUESTED FEDERAL ACTIONS}

\begin{enumerate}
\item \textbf{Grand Jury Authorization:} Impanel a federal grand jury for RICO and related civil rights investigation.
\item \textbf{FBI Coordination:} Joint investigation with the FBI Seattle Field Office Civil Rights squad.
\item \textbf{Prosecutorial Resources:} Assignment of experienced RICO and civil rights prosecutors.
\item \textbf{Witness Protection:} Consider protection for victims facing retaliation.
\item \textbf{Asset Seizure:} Preliminary restraining orders on enterprise assets.
\item \textbf{Interstate Coordination:} Joint investigation with the U.S. Attorney, Western District of Washington, and coordination with DOJ Public Integrity Section regarding potential public corruption charges.
\end{enumerate}

\section*{SUBMISSION CONTENTS (11 Documents)}

\begin{enumerate}
\item Case Summary.
\item FBI Seattle Field Office Civil Rights Cover Letter (Washington-focused).
\item FBI Montana Field Office Civil Rights Cover Letter (Montana-focused).
\item Montana Attorney General Cover Letter.
\item Washington Attorney General Cover Letter.
\item This U.S. Attorney, District of Montana Cover Letter.
\item U.S. Attorney, Western District of Washington Cover Letter.
\item DOJ Public Integrity Section Cover Letter.
\item Danielle Chard Criminal Report.
\item E'Lise Chard Criminal Report.
\item YWCA Institutional Corruption Supplemental, Elvis Nuno Sworn Declaration, and comprehensive evidentiary documentation.
\end{enumerate}

\section*{EVIDENTIARY STANDARD}

Documentation meets RICO and civil rights prosecution standards:

\begin{itemize}
\item Sworn declarations under penalty of perjury.
\item Official records (police reports, court filings, DOJ reports).
\item Findings from the 2012–2016 federal DOJ investigation indicate that the underlying institutional failures were never meaningfully corrected and that local actors have actively resisted operational transparency and external accountability.
\item Pattern evidence across multiple victims and 10+ year timeframe.
\item Financial records documenting fraud and damages.
\item Institutional records (ProPublica, federal grants).
\item Independent corroboration from multiple sources.
\end{itemize}

\section*{URGENCY}

\begin{itemize}
\item Statute of limitations approaching for some predicate acts.
\item Ongoing criminal activity affecting vulnerable populations.
\item Evidence preservation concerns.
\item Federal leadership essential (local accountability has failed).
\item Victim safety concerns.
\end{itemize}

We respectfully request an initial response via digital communication outlining appropriate next steps, sent to \texttt{advocacy@misjusticealliance.org}, so that grand jury authorization, investigation timeline, and coordination with the FBI and DOJ Public Integrity Section can proceed while protecting the anonymity and safety of MISJustice Alliance members and reporting victims; this packet reflects thousands of hours of collaborative work, extensive deep records research, and interviews with multiple victims, and the evidence is comprehensive and prosecution-ready for immediate grand jury presentation.

\vspace{0.3in}

\noindent
Respectfully submitted,

\vspace{0.3in}

\noindent
MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims

\vspace{0.2in}

\noindent
Contact: [\textit{Contact information will be provided only through MISJustice Alliance after the receiving office confirms a concrete plan to prevent any retaliation or adverse action against reporting victims and witnesses}]

\end{flushleft}

\end{document}
