\documentclass[12pt,oneside]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}

\begin{document}

\begin{flushleft}

MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims \\
\today

\vspace{0.3in}

Tessa M. Gorman \\
United States Attorney \\
Western District of Washington \\
United States Courthouse \\
700 Stewart Street, Suite 5220 \\
Seattle, WA 98101\footnote{Please confirm and update this address and name to the current U.S. Attorney before filing.}

\vspace{0.3in}

\textbf{RE: Federal Civil Rights and Public Corruption Prosecution Referral} \\
\textbf{18 U.S.C. § 242, § 371, § 1512; 42 U.S.C. § 1983, § 1985} \\
\textbf{King County Prosecutors, Seattle/Edmonds Police, Interstate Conspiracy with Montana} \\
\textbf{OPA Case 2016OPA-1167 Evidence Alteration and Pattern of Misconduct}

\vspace{0.3in}

Dear U.S. Attorney:

\vspace{0.2in}

MISJustice Alliance respectfully submits this federal criminal referral for investigation and potential prosecution of Washington-based actors involved in an interstate civil rights and public corruption scheme targeting Elvis Ryland Nuno and potentially other victims. The evidence demonstrates a multi-year pattern of false reporting, malicious prosecution, excessive bail, evidence alteration, and coordinated harassment involving King County prosecutors, Seattle and Edmonds law enforcement, and Montana-based co-conspirators.

\section*{FEDERAL JURISDICTION AND CASE SCOPE}

The Western District of Washington has jurisdiction over:

\begin{itemize}
\item \textbf{Washington-based conduct} by Danielle Christine Chard (Seattle/Edmonds resident), including perjury, false statements, and witness tampering.
\item \textbf{Actions by King County prosecutors} and Seattle/Edmonds law enforcement officials that deprived Mr. Nuno of rights secured by the Constitution and laws of the United States.
\item \textbf{Interstate conspiracy and coordination} with Montana law enforcement and prosecutors to pursue baseless charges, impose extreme bail conditions, and suppress exculpatory evidence.
\end{itemize}

Federal statutes implicated include 18 U.S.C. § 242 (deprivation of rights under color of law), § 371 (conspiracy), § 1512 (witness tampering/obstruction), false statements provisions, and related public corruption statutes, as well as civil rights conspiracy frameworks under 42 U.S.C. § 1983 and § 1985.

\section*{WASHINGTON-BASED CRIMINAL CONDUCT}

\subsection*{Danielle Christine Chard (Seattle/Edmonds)}

\begin{itemize}
\item Multi-year pattern of false reports to Seattle and Edmonds police departments.
\item Sworn statements and testimony contradicted by electronic records and third-party evidence.
\item Coordinated efforts with her twin sister, E'Lise Chard (in Montana), to engineer parallel false accusations in both states.
\end{itemize}

\subsection*{King County Prosecutors and Law Enforcement}

\begin{itemize}
\item Charges filed without probable cause based on demonstrably false factual narratives.
\item Excessive bail demands in the \$50,000--\$100,000 range for misdemeanor-level allegations, raising Eighth Amendment concerns.
\item Suppression or non-disclosure of exculpatory material and impeachment evidence, including known inconsistencies in complainant statements and police reports.
\item Coordination with Montana prosecutors to maintain parallel cases despite the lack of a legitimate jurisdictional nexus.
\end{itemize}

\subsection*{OPA Case 2016OPA-1167: Evidence Alteration}

The submission includes the full correspondence related to Seattle Office of Professional Accountability (OPA) Case 2016OPA-1167, in which:

\begin{itemize}
\item Mr. Nuno reported apparent falsification and alteration of police reports.
\item OPA acknowledged the existence of ``inconsistencies'' in the reports.
\item The case was closed without discipline, prosecution, or meaningful remedial action.
\end{itemize}

This sequence illustrates systemic accountability failure and tolerance of evidence irregularities in matters involving Mr. Nuno.

\section*{INTERSTATE CONSPIRACY WITH MONTANA ACTORS}

The Western District of Washington referral is part of a broader interstate scheme in which:

\begin{itemize}
\item Washington charges were filed based on false narratives originating from Montana.
\item Montana cases relied on Washington reports and charging decisions, creating a circular reinforcement loop.
\item Prosecutors and police in both states shared information in a manner that appears designed to evade scrutiny and chill Mr. Nuno's protected activities, rather than to vindicate legitimate law enforcement interests.
\end{itemize}

The coordinated pattern implicates civil rights conspiracy and public corruption concerns and will require close coordination with the U.S. Attorney for the District of Montana and the DOJ Criminal Division Public Integrity Section.

\section*{REQUESTED FEDERAL ACTIONS}

\begin{enumerate}
\item \textbf{Criminal Civil Rights Investigation:} Open an investigation into violations of 18 U.S.C. § 242 and related statutes by King County prosecutors and Washington law enforcement actors.
\item \textbf{Public Corruption Coordination:} Confer with the DOJ Criminal Division Public Integrity Section regarding potential prosecution of public officials and prosecutors whose conduct falls within PIN's jurisdiction.
\item \textbf{Grand Jury Consideration:} Consider impaneling a federal grand jury in the Western District of Washington to review evidence of false statements, obstruction, and civil rights violations.
\item \textbf{Interstate Coordination:} Coordinate closely with the U.S. Attorney, District of Montana, and the FBI Seattle Field Office to investigate the dual-jurisdiction conspiracy and information-sharing practices.
\item \textbf{Witness and Victim Protection:} Assess retaliation risks and implement appropriate protective measures for Mr. Nuno and any other witnesses who may come forward.
\end{enumerate}

\section*{SUBMISSION CONTENTS (11 Documents)}

\begin{enumerate}
\item Executive Summary / Case Summary.
\item FBI Seattle Field Office Civil Rights Cover Letter (Washington-focused).
\item FBI Montana Field Office Civil Rights Cover Letter (Montana-focused).
\item Montana Attorney General Cover Letter.
\item Washington Attorney General Cover Letter.
\item U.S. Attorney, District of Montana Cover Letter.
\item This U.S. Attorney, Western District of Washington Cover Letter.
\item DOJ Criminal Division Public Integrity Section Cover Letter.
\item Danielle Chard Criminal Report.
\item E'Lise Chard Criminal Report.
\item YWCA Institutional Corruption Supplemental, Elvis Nuno Sworn Declaration, and comprehensive evidentiary documentation.
\end{enumerate}

\section*{URGENCY}

The referral raises time-sensitive concerns including statutes of limitation for certain federal offenses, ongoing reputational and economic harm to Mr. Nuno, and potential continued misuse of Washington criminal justice resources in reliance on tainted information. Prompt investigative triage and coordination with federal and state partners is therefore requested.

\vspace{0.3in}

\noindent
Respectfully submitted,

\vspace{0.3in}

\noindent
MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims

\vspace{0.2in}

\noindent
Contact: [\textit{Contact information will be provided only through MISJustice Alliance after the receiving office confirms a concrete plan to prevent any retaliation or adverse action against reporting victims and witnesses}]

\end{flushleft}

\end{document}
