\documentclass[12pt,oneside]{article}

\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}

\begin{document}

\begin{flushleft}

MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims \\
\today

\vspace{0.3in}

Public Integrity Section \\
Criminal Division \\
U.S. Department of Justice \\
950 Pennsylvania Avenue, NW \\
Washington, DC 20530

\vspace{0.3in}

\textbf{RE: Public Corruption and Prosecutorial Misconduct Referral} \\
\textbf{Missoula County Attorney's Office, King County Prosecutors, Law Enforcement Officials} \\
\textbf{Interstate Abuse of Public Office, Civil Rights Deprivations, and Obstruction of Justice} \\
\textbf{Coordination with FBI Civil Rights, USAO District of Montana, and USAO Western District of Washington}

\vspace{0.3in}

Dear Public Integrity Section Chief:

\vspace{0.2in}

MISJustice Alliance respectfully submits this referral to the Public Integrity Section (PIN) regarding a decade-long pattern of alleged public corruption, prosecutorial misconduct, and abuse of law enforcement authority spanning Missoula County, Montana and King County, Washington. The evidence indicates that elected and appointed officials in local prosecutor's offices and police departments coordinated to pursue baseless criminal charges, suppress exculpatory information, and retaliate against protected speech by Elvis Ryland Nuno and potentially other victims.

\section*{PIN JURISDICTION AND CASE PROFILE}

The reported conduct falls squarely within PIN's core jurisdiction:

\begin{itemize}
\item \textbf{State and local public corruption:} Involving county prosecutors, law enforcement supervisors, and officials wielding public authority.
\item \textbf{Prosecutorial misconduct:} Including charging without probable cause, suppression of exculpatory evidence, and retaliatory use of criminal process.
\item \textbf{Abuse of public trust and office:} Leveraging prosecutorial and police powers to enforce a coordinated defamation and harassment campaign.
\item \textbf{Election and appointment-related implications:} Potential impact on the integrity of offices staffed by elected or politically appointed officials.
\end{itemize}

Given the involvement of multiple local prosecutors' offices and police departments across two states, and the potential for conflicts of interest or reluctance to pursue charges locally, PIN's oversight and coordination role is critical.

\section*{KEY INSTITUTIONAL ACTORS}

\subsection*{Missoula County, Montana}

\begin{itemize}
\item Missoula County Attorney's Office: Repeatedly pursued charges against Mr. Nuno in reliance on demonstrably false narratives tied to YWCA Missoula staff and allied law enforcement officers.
\item Missoula Police Department: Engaged in warrantless searches, questionable arrests, and close coordination with YWCA Missoula where a sitting detective simultaneously served on the YWCA Board.
\end{itemize}

\subsection*{King County, Washington}

\begin{itemize}
\item King County Prosecutors: Filed and maintained charges in Seattle/Edmonds matters despite clear evidentiary deficiencies and acknowledged inconsistencies in police reporting.
\item Local law enforcement (Seattle and Edmonds): Generated reports later identified as inconsistent or altered, with oversight failures documented in OPA Case 2016OPA-1167.
\end{itemize}

\section*{PATTERN OF PUBLIC CORRUPTION AND MISCONDUCT}

Across Montana and Washington, the evidence reflects:

\begin{itemize}
\item \textbf{Systematic misuse of charging discretion} to advance a coordinated narrative originating from private complainants (Danielle and E'Lise Chard) with institutional ties to YWCA Missoula.
\item \textbf{Suppression and non-disclosure of exculpatory information} to defense counsel and courts, including known inconsistencies in complainant accounts and police documentation.
\item \textbf{Excessive bail practices} in Washington (e.g., demands in the \$50,000--\$100,000 range for non-violent misdemeanor charges) that appear designed to coerce, intimidate, and incapacitate rather than ensure appearance.
\item \textbf{Interstate coordination} whereby prosecutors and police in one state relied on the other's proceedings and reports to justify continued harassment, creating a self-reinforcing appearance of legitimacy.
\item \textbf{Retaliation against protected activity}, including Mr. Nuno's 2018 formal complaint to YWCA Missoula and subsequent public criticism of institutional misconduct.
\end{itemize}

This constellation of actions suggests an abuse of public office and a breakdown of ordinary checks and balances in both local systems, warranting centralized review by PIN.

\section*{RELATIONSHIP TO PARALLEL FEDERAL REFERRALS}

This PIN referral is being submitted in parallel with:

\begin{itemize}
\item A comprehensive civil rights and RICO referral to the \textbf{FBI Seattle Field Office Civil Rights squad}.
\item Prosecution-focused referrals to the \textbf{U.S. Attorney's Office for the District of Montana} and the \textbf{U.S. Attorney's Office for the Western District of Washington}.
\item State-level referrals to the \textbf{Montana Attorney General (Criminal Division)} and the \textbf{Washington Attorney General (Civil Rights Division)}.
\end{itemize}

PIN's involvement is requested to:

\begin{itemize}
\item Provide expert guidance and oversight regarding public corruption and prosecutorial misconduct issues arising from these facts.
\item Ensure that investigations by USAOs and the FBI fully account for potential criminal liability of state and local officials, including prosecutors, consistent with Department policies.
\item Help resolve any questions about venue, coordination, or conflicts of interest across districts.
\end{itemize}

\section*{REQUESTED ACTIONS}

\begin{enumerate}
\item \textbf{Intake and Assessment:} Review the accompanying Executive Summary, individual perpetrator reports, and evidentiary documentation to determine whether the facts warrant a formal PIN investigation.
\item \textbf{Coordination with USAOs and FBI:} Engage with the District of Montana, Western District of Washington, and the FBI Seattle Field Office regarding potential charges against state and local officials.
\item \textbf{Guidance on Prosecutorial Misconduct Issues:} Advise on the appropriate handling of allegations involving charging without probable cause, Brady violations, and retaliatory use of criminal process.
\item \textbf{Evaluation of Public Corruption Charges:} Consider application of federal public corruption statutes to conduct by prosecutors and police supervisors in both states.
\item \textbf{Protection of Complainant and Witnesses:} Coordinate with investigative components to address retaliation risks arising from Mr. Nuno's continued cooperation.
\end{enumerate}

\section*{SUBMISSION CONTENTS (11 Documents)}

\begin{enumerate}
\item Case Summary (institutional corruption and civil rights violations, 2015--2025).
\item FBI Seattle Field Office Civil Rights Cover Letter (Washington-focused).
\item FBI Montana Field Office Civil Rights Cover Letter (Montana-focused).
\item Montana Attorney General Cover Letter.
\item Washington Attorney General Cover Letter.
\item U.S. Attorney, District of Montana Cover Letter.
\item U.S. Attorney, Western District of Washington Cover Letter.
\item This Public Integrity Section Cover Letter.
\item Danielle Chard Criminal Report.
\item E'Lise Chard Criminal Report.
\item YWCA Institutional Corruption Supplemental, Elvis Nuno Sworn Declaration, and comprehensive evidentiary documentation (police reports, court records, correspondence).
\end{enumerate}

\section*{URGENCY}

Given ongoing harm to Mr. Nuno, the potential for continuing misuse of prosecutorial and police authority, and the approaching limitations periods for certain offenses, timely review by the Public Integrity Section is essential. MISJustice Alliance stands ready to facilitate secure transmission of additional materials at your request.

\vspace{0.3in}

\noindent
Respectfully submitted,

\vspace{0.3in}

\noindent
MISJustice Alliance \\
On behalf of Elvis Ryland Nuno and other victims

\vspace{0.2in}

\noindent
Contact: [\textit{Contact information will be provided only through MISJustice Alliance after the receiving office confirms a concrete plan to prevent any retaliation or adverse action against reporting victims and witnesses}]

\end{flushleft}

\end{document}
